### 2015-07-18 motivation.tex
Tighten more.

\paragraph{Gaps in current practice}
The cryptographic versioning of Nix and HashDist is very flexible. It versions
the package {\it and} its dependency configuration, and can represent any
configuration. However, users cannot navigate or query the installed software.
The systems are in a sense ``write-only'':
Nix does not offer a way to view a package's dependencies.
%
EasyBuild and Smithy generate environment modules, which allow querying
through their own interface. Naming schemes used in existing module systems, however, cannot
handle combinatorial versions. The Lmod authors call this the
``matrix problem``~\cite{mclay:lmod-tutorial}.

@@

The main limitation of existing tools is the lack of build {\it composability}.
The full set of package versions is combinatorial, and realizing an arbitrary
combination of compiler, MPI version, build options, and dependency versions
requires tediously modifying many package files.
Indeed, the number of package files required for most existing systems scales
with the number of version {\it combinations}, not the number of packages, which
quickly becomes unmanageable.  As an example, the very flexible EasyBuild
system has over 3,300 files for several permutations of only 600 packages.
To create a slightly different dependency graph, an entire new package file
hierarchy must be constructed.  HashDist a more robust support for composition,
but it does not have a first-class parameters for package versions, compilers,
or versioned interfaces.
%
HPC sites need better mechanisms to {\it parameterize} packages so that new
builds can be {\it composed} in response to user needs.
%

>>>>

\paragraph{Gaps in current practice}
The cryptographic versioning of Nix and HashDist is very flexible. It versions
the package {\it and} its dependency configuration, and can represent any
configuration. However, users cannot navigate or easily query the installed
software.
%The systems are in a sense ``write-only'':
%Nix does not offer a way to view a package's dependencies.
%
EasyBuild and Smithy generate environment modules, and some querying is
possible through the module system.  Naming schemes used in existing module
systems, however, cannot handle combinatorial versions. The Lmod authors
call this the ``matrix problem''~\cite{mclay:lmod-tutorial}.

@@

The main limitation of existing tools is the lack of build {\it composability}.
The full set of package versions is combinatorial, and realizing an arbitrary
combination of compiler, MPI version, build options, and dependency versions
requires tediously modifying many package files.
Indeed, the number of package files required for most existing systems scales
with the number of version {\it combinations}, not the number of packages, which
quickly becomes unmanageable.  As an example, the EasyBuild
system has over 3,300 files for several permutations of only 600 packages.
A slightly different dependency graph requires an entire new package file
hierarchy.  HashDist a more robust support for composition,
but it does not have a first-class parameters for versions, compilers,
or versioned interfaces.
%
HPC sites need better mechanisms to {\it parameterize} packages so that new
builds can be {\it composed} in response to user needs.
%
